Figures for 3-D printed oxygen devices

### 2015-03-06 publishing/latex/plos_template.tex
working on disscussion

@@

Future directions: more channel networks, higher format plates, stackable plates with gas connections

>>>>

This device provides convient oxygen control within a standard culture format.
This device adds oxygen control will still allowing standard assays and imageing to occur, with the additon of a source of the gas of interest.
3D-printing allows this design to be shared directly and modified by and end user without learning any microfabrication techniques.

The device is also resuable. Typical microfulidic chips for the control of oxygen conditions are single use due to biological material fouling the gas pereapilty. 
Due the the addheasive aplication of the membranes the have be easily removed and replaced with fresh ones allowing the device to be reused. 
It is also convienat that the cell are not grow in the device.

@@

Future directions: more channel networks, higher format plates, stackable plates with gas connections
With the 3D printhing higher levels of intrececy can be achieved without complating fabrication.
This allows any number of addtional features to be added.
An on device mixer that could supply different levels of mixing between two sources of gas could reduce the number of tanks required.
A mixer could also allow more conditions in a single plate perhaps even 1 per well or even gradients within wells.
Even hight format plates such as 96 well plates could be used.
Gas connections could be reloated to allow stacking of device in incubators.
